\Large{Adversarial Training against Systematic Uncertainty}

### 2016-09-29 tex/paper.tex
save

In high energy physics, systematic uncertainties represent our incomplete
knowledge in the simulation of physical processes or in the properties of the
detection apparatus. In effect, these uncertainties typically cause variations
in the conditional distributions of the data, thereby altering the decisions
and resulting efficacy of a classifier trained from it. In this work, we
repurpose adversarial training as a means to learn a pivotal classifier which is
invariant to variations of the nuisance parameters describing the effects of
systematic uncertainties. In machine learning, this problem is closely related
to those of domain adaptation and enforcing fairness in classification.
Following that line of work, the proposed method can be regarded as
generalization that also supports the continuous case, which can be viewed as
handling infinitely many domains or as enforcing fairness over continuous
features.

>>>>

In high energy physics, systematic uncertainties represent our incomplete
knowledge in the simulation of physical processes or in the properties of the
detection apparatus. In effect, these uncertainties typically cause variations
in the conditional distributions of the data, thereby altering the decisions and
resulting efficacy of a classifier trained from it. To accomodate for this, we
repurpose adversarial training as a means to learn a pivotal classifier which is
invariant to variations of the nuisance parameters describing the effects of
systematic uncertainties. In particular, we show and derive theoretical
conditions under which classification optimality and invariance with respect to
systematics can be achieved, which we confirm experimentally on a couple of
illustrative examples. In machine learning, this problem is closely related to
those of domain adaptation and enforcing fairness in classification. Following
that line of work, the proposed method can be regarded as generalization that
also supports the continuous case, which can be viewed as handling infinitely
many domains or as enforcing fairness over continuous features.
